# ggunileg

I often face the problem of wanting to visually distinguish data with dozens of distinct groups, in which case color scales often become uninformative.

```{r}
library(ggplot2)
some_data <- data.frame(x = 1:100 + runif(n = 100, min = -10, max = 10), y = 1:100 + runif(n = 100, min = -10, max = 10), colorLabel = sample(letters[1:20], size = 100, replace = T))
bad_plot <- ggplot(data = some_data, aes(x = x, y = y, color = colorLabel)) +
  geom_point() +
  theme_bw() +
  guides(color = guide_legend(ncol = 2))
bad_plot
```

One potential solution is to combine color- and shape scales, but this is not really helpful out of the because the legends are not combined by default, so mapping invidiual points to their color- and shape value by eye is cumbersome at best.

```{r}
some_data$shapeLabel <- as.factor(sample(1:5, size = dim(some_data)[1], replace = TRUE))
still_bad_plot <- ggplot(data = some_data, aes(x = x, y = y, color = colorLabel, shape = shapeLabel)) +
  geom_point() +
  theme_bw() +
  guides(color = guide_legend(ncol = 2))
still_bad_plot
```

To fix this I offer the `scale_color_highres` function as a convenience function. The number of distinct shape levels can be controlled using the `numShapeLevels` parameter. Note how the colorLabel variable is mapped to both color and shape aesthetics here.

```{r}
library(ggunileg)
useful_plot <- ggplot(data = some_data, aes(x = x, y = y, color = colorLabel, shape = colorLabel)) +
  geom_point() +
  theme_bw() +
  scale_color_highres(numShapeLevels = 5, name = 'newLegendTitle') +
  guides(color = guide_legend(ncol = 2), shape = guide_legend(ncol = 2))
useful_plot
```

